# Reproducible Research: Peer Assessment 1
---
<br/>

## Loading and preprocessing the data
<br/>

Read activity.csv into a data frame and view some rows
```{r}
df <- read.csv("activity.csv")
df[2303:2313,]
```
<br/>

And for good measure - a summary view...
```{r}
summary(df)
```
<br/>

Structure of data frame df
```{r}
str(df)
```
(note the NAs)
<br/>
<br/>

Create a new, clean data frame without the NAs, reset the factor  
levels and compare it to the structure of the original df
```{r}
cdf <- df[! is.na(df$steps), ]
cdf$date <- cdf$date[, drop=TRUE]
str(cdf)
```
Nice and clean... We're good to go.

<br/>
## What is mean total number of steps taken per day?
<br/>
Histogram of the total number of steps taken each day
```{r}
hist(as.vector(tapply(cdf$steps, list(cdf$date), FUN=sum)), xlab="No of steps per day", ylab="Frequency / No of days", main="Total Number of Steps Taken Each day")
```
<br/>
Mean number of steps per day
```{r}
hist(as.vector(tapply(cdf$steps, list(cdf$date), FUN=mean)), xlab="Mean steps per day", ylab="Frequency / No of days", main="Average (Mean) Number of Steps Per day")
```
<br/>
The large number of zeroes (0) per day gives a median of 0 on day variables
```{r}
as.vector(tapply(cdf$steps, list(cdf$date), FUN=median))
```
<br/>
## What is the average daily activity pattern?
<br/>

Time series plot of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
msteps <- aggregate(cdf$steps, by=list(cdf$interval), mean)
plot(msteps$Group.1, msteps$x, type="l", main="Mean No. of Steps per Interval Accross all Days", xlab="Daily 5 Minute Intervals", ylab="No. of Steps")
```
<br/>

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
msteps$Group.1[which.max(msteps$x)]
```
<br/>
<br/>

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?


